Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-12 GWLDCII.tex
paper 2 readthrough, sections 1 through 4

% for highlighting regions of a diagram edge
\tikzstyle{linehighlight}=[red,line width = 3pt,line cap = round, draw opacity = 0.5]

@@

This paper is the second in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory. This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian. This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.

@@

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is to enumerate (without identifying) the positroid cells that associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.

In recent years, there has been significant interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, galashinlam, AmplituhedronDecomposition}. This started with the observation that BCFW diagrams, which represent the on shell interactions of this theory, correspond to plabic graphs \cite{GrassmannAmplitudebook}. Plabic graphs were introduced by Postnikov in \cite{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$. This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}. Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron. This both gives a novel and elegant interpretation of scattering Amplitudes for this theory, as well as a means of simplifying the calculations greatly from traditional Feynman diagram approaches. Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}. The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space. For instance, it is conjectured that the Amplituhedron is orientable, whereas the first author and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. This is not too alarming, as it is conjectured the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.

This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \cite{Arkani-Hamed:2013jha}. Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.

As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum. This has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto. In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.

@@

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators which must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

The entries $c_{p,q}$ are non-zero real variables. Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with. See \ref{integraldetails} for an example of a diagram $W$ and its associated matrix.

The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ associated to the $W$, which we denote by $\Sigma(W)$ \cite{wilsonloop}. Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$.

@@

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}. The volume form is written in terms of the elements of $C(W)$ as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \]
The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.

For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size. By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e. we have \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty. \eas

In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum. In particular, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}. This has been checked for particular classes of examples (e.g. \cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.

@@

\begin{dfn}\label{def R(W)}
Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$. Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is. Define 
\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
to be the component of $R(W)$ associated to edge $e$. Note that if $r = 1$ (i.e. there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$. If $r=0$, set $R_e = 1$. The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e. 
\[R(W) = \prod_{e \in V} R_e.\]
\end{dfn}

In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$. In fact, it can be read directly off of $C(W)$, in terms of characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}). We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.

@@

To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\end{eg}

@@

By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$. Each term $I_i$ is simply the minimal (with respect to the $<_i$-lex order) basis of the positroid. A characterization of all bases of the positroid in terms of the Grassmann necklace and the Gale order was given by Oh in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
\ba \cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}. \label{basesofmatroids}\ea
Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.

\begin{dfn}\label{def:le diagram}
A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) mustbasesofmatroids\ also contain a $0$, or both.
\end{dfn}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram with $k$ propagators, and $C(W)$ the associated matrix defined in \eqref{C(W) dfn}. Let $M(W)$ be the matroid realized by $C(W)$, i.e. the matroid with ground set $[n]$ whose independent sets are exactly the sets $V \subseteq [n]$ such that the columns of $C(W)$ indexed by $V$ are linearly independent.

In \cite{wilsonloop}, Agarwala and Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:

@@

Forgetting about the matroid and simply thinking about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows: because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns. Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.  Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
\end{proof}

@@

By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.

However, in order to identify the positroid associated to a given Wilson loop diagram $W$ we first have to construct $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}. Alternatively, one could obtain the decorated permutation of the positroid from $C(W)$ as in \hlfix{[ref]}{Sian needs to go find this reference} and then convert it into a Grassmann necklace as described in \cite[Section 16]{Postnikov}.

In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices. Even in this simple case, we see that the mapping from admissible WLD to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.

@@

We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and either:
\begin{itemize}
\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
  %a configuration \eqref{eq:2 prop config} in $D$
{\em or} 
\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
	\begin{scope}
	\drawWLDfragment[10]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\centerarc[linehighlight](0,0)(\zero + 1.5*\step:\zero + 2.35*\step:\radius)
	\newnode{1}{}
	\newnode{3}{}
	\newnode{4}{}
	\newnode{5}{}
	\newnode[below]{9}{i_1}
	\newnode{10}{}
	\newprop[midway,above]{1.4}{9.5}{\footnotesize $q_1$}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\newpropbend{2.3}{4.7}{60}
		\node at (\zero + 3.5*\step:\radius*0.78) {\footnotesize $p_1$};
	\end{scope}
\node[align = center] at (\zero +1.7*\step:\radius*1.4) {\footnotesize \em 0, 1, or 2 \\ \footnotesize \em vertices in \\ \footnotesize \em this region};
\node at (\zero + 10*\step:\radius*0.3) {$\cP_{in}(q_1)$};
\end{scope}
\end{tikzpicture}
\]
\caption{The base case of the induction in Lemma~\ref{lem sian}.}\label{fig base case lem sian} \end{figure}

@@

Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses. Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e. we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.

>>>>

% for highlighting regions of a diagram edge
\tikzstyle{linehighlight}=[blue,line width = 3pt,line cap = round, draw opacity = 0.5]

@@

This paper is the second in a two part series investigating the combinatorics and geometry underlying Wilson loop diagrams in SYM $N=4$ theory. This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian. This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannian.

@@

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell under this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.}

In recent years, there has been significant interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, galashinlam, AmplituhedronDecomposition}. This started with the observation that BCFW diagrams, which represent the on shell interactions of this theory, correspond to plabic graphs \cite{GrassmannAmplitudebook}. Plabic graphs were introduced by Postnikov in \cite{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$. This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}. Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron. This both gives a novel and elegant interpretation of scattering amplitudes for this theory, as well as a means of greatly simplifying the calculations involved in traditional Feynman diagram approaches. Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}. Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space. For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. This is not too alarming, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.

This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.

As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum. This has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto. In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.

@@

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

The entries $c_{p,q}$ are non-zero real variables. Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with. See Example~\ref{integraldetails} for an example of a diagram $W$ and its associated matrix.

The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}. Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.

@@

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}. The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;, \end{equation}
where the denominator $R(W)$ is given in Definition~\ref{def R(W)} below. The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.

For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size. By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e. we have 
\bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas

In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum. Specifically, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}. This has been checked for particular classes of examples (e.g. \cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.

@@

\begin{dfn}\label{def R(W)}
Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$. Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ is closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is. Define the polynomial
\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
to be the component of $R(W)$ associated to edge $e$. Note that if $r = 1$ (i.e. there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$. If $r=0$, set $R_e = 1$. The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e. 
\[R(W) = \prod_{e \in V} R_e.\]
\end{dfn}

In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$. In fact, it can be read directly off of $C(W)$, in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}). We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.

@@

To calculate $R(W)$, we first compute the polynomials associated to each edge of $W$: \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram (recall equation~\eqref{eq:omega(W) def}) is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\end{eg}

@@

By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$. Each term $I_i$ is simply the minimal (with respect to the $<_i$-lex order) basis of the positroid. A characterization of all bases of the positroid in terms of the Grassmann necklace and the Gale order was given by Oh in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
\ba \cB = \left\{J \in \binom{[n]}{k}\ \Big|\ I_i \gale{i} J \ \ \forall i \in [n]\right\}. \label{basesofmatroids}\ea
Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.

\begin{dfn}\label{def:le diagram}
A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) must also contain a $0$, or both.
\end{dfn}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram with $k$ propagators, and $C(W)$ the associated matrix defined in equation~\eqref{C(W) dfn}. Let $M(W)$ be the matroid realized by $C(W)$, i.e. the matroid with ground set $[n]$ whose independent sets are exactly the sets $V \subseteq [n]$ such that the columns of $C(W)$ indexed by $V$ are linearly independent.

In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:

@@

  Alternatively if we forget about the matroid and simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.

  Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns. Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.  Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
\end{proof}

@@

By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.

However, in order to identify the positroid associated to a given Wilson loop diagram $W$ we first have to construct $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}. In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices. Even in this simple case, we see that the mapping from admissible WLD to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.

@@

We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and such that either:
\begin{itemize}
\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
  %a configuration \eqref{eq:2 prop config} in $D$
{\em or} 
\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
	\begin{scope}
	\drawWLDfragment[10]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\centerarc[linehighlight](0,0)(\zero + 1.5*\step:\zero + 2.35*\step:\radius)
	\newnode{1}{}
	\newnode{3}{}
	\newnode{4}{}
	\newnode{5}{}
	\newnode[below]{9}{i_1}
	\newnode{10}{}
	\newprop[midway,above]{1.4}{9.5}{\footnotesize $q_1$}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\newpropbend{2.3}{4.7}{60}
		\node at (\zero + 3.5*\step:\radius*0.78) {\footnotesize $p_1$};
	\end{scope}
\node[align = center] at (\zero +1.7*\step:\radius*1.4) {\footnotesize \em 0, 1, or 2 \\ \footnotesize \em vertices in \\ \footnotesize \em this region};
\node[gray] at (\zero + 10*\step:\radius*0.4) {\footnotesize$\cP_{in}(q_1,<_{i_1})$};
\node[gray] at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $\cP_{out}(q_1,<_{i_1})$};
\end{scope}
\end{tikzpicture}
\]
\caption{The base case of the induction in Lemma~\ref{lem sian}.}\label{fig base case lem sian} \end{figure}

@@

Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses. (See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e. we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.

\begin{figure}[h]
\vspace{1cm}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[15]{4}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i_r}
	\newnode[left]{2}{i_r+1}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode[right]{14}{k_r}
	\newnode[right]{15}{k_r+1}
	\newprop[midway,above]{1.5}{14.5}{\footnotesize $q_r$}
	\draw[smallpropagator,gray] (\zero+2.5*\step:\radius) -- (\zero + 12.5*\step:\radius) node[midway,above,gray] {\footnotesize $q_{r}'$};
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\newpropbend{5.2}{7.7}{80}
		\node at (\zero + 6.5*\step:\radius*0.85) {\footnotesize $p_{r+1}$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{We can replace $q_r$ with $q'_r$ as long as $q_r$ and $p_{r+1}$ are on opposite sides of $q'_r$.}
\label{fig smallest q in lem sian}
\end{figure}
